---
title: "p8105_hw6_ww2579"
author: "Wenzhao Wu"
date: "11/24/2020"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(modelr)
library(p8105.datasets)

set.seed(1)

knitr::opts_chunk$set(
  fig.width = 12,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1

```{r}
homicide_df = 
  read_csv("data/homicide_data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```

Start with one city.

```{r}
baltimore_df = 
  homicide_df %>%
  filter(city_state == "Baltimore, MD")

glm(resolution ~ victim_age + victim_sex + victim_race, data = baltimore_df,family = binomial()) %>%
  broom::tidy() %>%
  mutate(
    OR = exp(estimate),
    CL_lower = exp(estimate - 1.96 * std.error),
    CL_upper = exp(estimate + 1.96 * std.error)) %>%
  select(term, OR, starts_with(("CI"))) %>%
  knitr::kable(digits = 3)
```

Try this across cities.

```{r}
models_results_df = 
  homicide_df %>%
  nest(data = -city_state) %>%
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)) %>%
  select(city_state, results) %>%
  unnest(results) %>%
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)) %>%
  select(city_state, term, OR, starts_with(("CI")))
```

Make a plot of city_state vs OR.

```{r}
models_results_df %>%
  filter(term == "victim_sexMale") %>%
  mutate(city_state = fct_reorder(city_state, OR)) %>%
  ggplot(aes(x = city_state, y = OR)) +
  geom_point() +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) +
  theme(axis.title.x = element_text(angle = 90, hjust = 1))
```

# Problem 2

Import and tidy the raw data.

```{r}
bwt_df = read.csv("./data/birthweight.csv") %>%
  mutate(babysex = as.factor(babysex),
         frace = as.factor(frace),
         malform = as.factor(malform),
         mrace = as.factor(mrace),
         parity = as.factor(parity)) %>%
  filter(parity != 3,
         parity != 6)
# Parity levels of 3 and 6 get removed because they contain only one observation, when I do the cross-validation step, errors would occur if the two single observations are included in the model.

```


Fit a regression model for birthweight.

```{r}
fit_bwt = lm(bwt~babysex + bhead + blength + delwt + fincome + frace + gaweeks + malform + menarche + mheight + momage + mrace + parity + pnumlbw + pnumsga + ppbmi + ppwt + smoken + wtgain, data = bwt_df)

step(fit_bwt, direction = "backward")

multi10_fit = lm(bwt~babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + ppwt + smoken, data = bwt_df)

multi3_fit = lm(bwt~babysex + bhead + blength, data = bwt_df)
# Criterion-based procedures
AIC(fit_bwt)
AIC(multi3_fit)
AIC(multi10_fit)
```

First, I fitted all variables in a MLR model, and apply stepwise regression to select predictors for the "best" model. Then I used the criterion-based procedures to check for AIC. Compared to the values of AIC from the full model (19 predictors) and 3-predictor model, the model obtained from the stepwise elimination has the smallest AIC. 

Selected predictors: babysex, bhead, blength, delwt, fincome, gaweeks, mheight, mrace, ppwt, smoken. 

Plot model residuals vs fitted values.

```{r}
new_df = bwt_df %>%
  add_predictions(multi10_fit) %>%
  add_residuals(multi10_fit)

resid_pred_plt = 
  new_df %>%
  ggplot(aes(x = pred, y = resid)) +
  geom_point() +
  geom_smooth(method = "lm", se = F)

resid_pred_plt
```


The second fitted model:

```{r}
fit2 = lm(bwt~blength + gaweeks, data = bwt_df)
```

The third fitted model:

```{r}
fit3 = lm(bwt~babysex + bhead + blength + babysex*bhead + babysex*blength + babysex*bhead*blength, data = bwt_df)
```


Compare 3 models above using cross validation.

```{r}
cv_df = crossv_mc(bwt_df,100)
cv_df =
  cv_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

    
cv_df = 
  cv_df %>% 
  mutate(  
    fit1 = map(train, ~lm(data = .x, bwt~babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + ppwt + smoken)), 
    fit2 = map(train, ~lm(bwt~blength + gaweeks, data = .x)),
    fit3 = map(train, ~lm(bwt~babysex + bhead + blength + babysex*bhead + babysex*blength + babysex*bhead*blength, data = .x))) %>% 
  mutate(rmse_fit1 = map2(fit1, test, ~rmse(model = .x, data = .y)), 
         rmse_fit2 = map2(fit2, test, ~rmse(model = .x, data = .y)),
         rmse_fit3 = map2(fit3, test, ~rmse(model = .x, data = .y)))

cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>%
  unnest(rmse) %>%
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin() +
  labs(
    title = "Prediction Error Distributions"
  )
```

**Comments:**
